Output Summary

### 2022-01-05 03-post-process/output-plots.Rmd
Suppress messages regarding removal of nodes

```{r make-diag-post, message = FALSE}
# make a reduced diagnostic posterior: drop out all quantities associated with simulated years
# there is no point in calculating diagnostic summaries for future years
if (length(simulated) > 0) {
  diag_post = post_remove(post, paste0("[", simulated), ask = FALSE)
} else {
  diag_post = post
}
```

>>>>

```{r make-diag-post}
# make a reduced diagnostic posterior: drop out all quantities associated with simulated years
# there is no point in calculating diagnostic summaries for future years
if (length(simulated) > 0) {
  diag_post = suppressMessages(post_remove(post, paste0("[", simulated), ask = FALSE))
} else {
  diag_post = post
}
```
